The \dealii{} Library, Version 9.2

### 2020-05-29 9.2/paper.tex
add a small section on our ternary operator support for VectorizedArray

The class \texttt{VectorizedArray<Number>} is a key component to achieve the high
node-level performance of the matrix-free algorithms in \dealii{}~\cite{KronbichlerKormann2012, KronbichlerKormann2019}. It is a wrapper
class around a short vector of $n$ entries of type \texttt{Number} and maps
arithmetic operations to appropriate single-instruction/multiple-data (SIMD)
concepts by intrinsic functions.
The class \texttt{VectorizedArray} has been made more user-friendly in this release by making
it compatible with the STL algorithms found in the header \texttt{<algorithm>}.
The length of the  vector can now be queried by  \texttt{VectorizedArray::size()} and its underlying number type by \texttt{VectorizedArray::value\_type}.
Furthermore, the \texttt{VectorizedArray} class now supports range-based iteration over its entries.

>>>>

The class \texttt{VectorizedArray<Number>} is a key component to achieve
the high node-level performance of the matrix-free algorithms in
\dealii{}~\cite{KronbichlerKormann2012, KronbichlerKormann2019}. It is a
wrapper class around a short vector of $n$ entries of type \texttt{Number}
and maps arithmetic operations to appropriate
single-instruction/multiple-data (SIMD) concepts by intrinsic functions.
The class \texttt{VectorizedArray} has been made more user-friendly in this
release by making it compatible with the STL algorithms found in the header
\texttt{<algorithm>}. The length of the  vector can now be queried by
\texttt{VectorizedArray::size()} and its underlying number type by
\texttt{VectorizedArray::value\_type}. The \texttt{VectorizedArray} class
now supports range-based iteration over its entries. In addition \dealii{}
now supports ternary operations on vectorized data, where for a given
binary comparison operation a true or false value is selected. For example,
the vectorized equivalent of \texttt{(left < right) ? true\_value :
false\_value} can be expressed as
\begin{c++}
auto result = compare_and_apply_mask<SIMDComparison::less_than>(
  left, right, true_value, false_value);
\end{c++}
which compares every element of the vectorized array individually and
selects the corresponding value from the \texttt{true\_value}, or
\texttt{false\_value} array.
